### 2019-03-19 outline/outline.tex
Initial commit

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[format=plain, font=it]{caption}
\usepackage{mathpazo}
\usepackage{biblatex}

\begin{document}

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
	\center

	\textsc{\LARGE University of Minnesota}\\[0.35cm]
	\textsc{\Large SENG 5852}\\[1.5cm]

	{\huge\bfseries Analysis of Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
	\textsc{\Large Research Paper Outline}\\[1cm]

	\textsc{\large\author
		LLue Xiong\\
	}

	\vfill\vfill\vfill
	\large\today
	\vfill
\end{titlepage}

\newpage
\section{Abstract}

\section{Introduction}
\subsection{Thesis Statement}
\subsection{Purpose}

\section{Body}
	\subsection{Differences of Interpretation \& Implementation}
	\subsection{What is Continuous Integration, Delivery, \& Deployment}
		\subsubsection{Inherently Agile}
		\subsubsection{Continuous Integration}
		\subsubsection{Continuous Delivery}
		\subsubsection{Continuous Deployment}
	\subsection{Struggles of Traceability}
	\subsection{Paradigm Shift in Leadership}

\section{Conclusion}

\section{Bibliography}
\begin{thebibliography}{6}
	\bibitem{Atkinson, Edwards} Atkinson, B., \& Edwards, D. (2018). Generic Pipelines Using Docker: The DevOps Guide to Building Reusable, Platform Agnostic CI/CD Frameworks. Berkeley, CA: Apress. doi:\\\texttt{https://doi.org/10.1007/978-1-4842-3655-0}
	\bibitem{Bosch} Bosch, J. (2014). Continuous Software Engineering. Cham: Springer International Publishing. doi:\\\texttt{https://doi-org.ezp1.lib.umn.edu/10.1007/978-3-319-11283-1.}
	\bibitem{Shahin, Babar, Zhu} Shahin, M., Babar, M. A., \& Zhu, L. (2017). Continuous Integration, Delivery and Deployment: A Systematic Review on Approaches, Tools, Challenges and Practices. IEEE Access, 5, 3909-3943. doi:\\\texttt{10.1109/access.2017.2685629}
	\bibitem{Stahl} St\aa hl, D. (2017). Large Scale Continuous Integration and Delivery: Making Great Software Better and Faster. [Groningen]: University of Groningen.
	\bibitem{Stahl, Hallen, Bosch} St\aa hl, D., Hall\'{e}n, K., \& Bosch, J. (2016). Achieving traceability in large scale continuous integration and delivery deployment, usage and validation of the eiffel framework. Empirical Software Engineering, 22(3), 967-995. doi:\\\texttt{10.1007/s10664-016-9457-1}
\end{thebibliography}

\end{document}

### 2019-03-19 outline/outline.tex
Add thesis/purpose statement

@@
 
-	{\huge\bfseries Analysis of Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
+	{\huge\bfseries The Race to Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
 	\textsc{\Large Research Paper Outline}\\[1cm]
@@
 \newpage
-\section{Abstract}
 
 \section{Introduction}
+
 \subsection{Thesis Statement}
-\subsection{Purpose}
+The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software development.
+
+\subsection{Purpose Statement}
+Software engineering has for two decades, contemplated and experimented with the concept of distributing software faster and better, without sacrificing reliability and security.
+There is a widespread movement in the technical community to advocate for using Agile practices to achieve such a feat, and in particular: continuous integration, delivery, and deployment.
+The traditional methods of software development no longer meets the need of businesses that want to proactively engage and retain customers.
+The organizational transition to Agile practices demands a large mentality change, understanding software as small increments developed with cross-collaboration of small team units as opposed to large modules developed by extensive siloed units.
 
@@
 	\subsection{Paradigm Shift in Leadership}
+	naturally forming resistance from individuals from within.
 
@@
 
+\newpage
 \section{Bibliography}
@@
 	\bibitem{Bosch} Bosch, J. (2014). Continuous Software Engineering. Cham: Springer International Publishing. doi:\\\texttt{https://doi-org.ezp1.lib.umn.edu/10.1007/978-3-319-11283-1.}
+	\bibitem{Stackify} Continuous Delivery, Deployment \& Integration: 20 Key Differences.
+(2018, June 04).
+Retrieved from \\\texttt{https://stackify.com/continuous-delivery-vs-continuous-\\deployment-vs-continuous-integration}
 	\bibitem{Shahin, Babar, Zhu} Shahin, M., Babar, M.

### 2019-03-20 outline/outline.tex
Add outline draft

--- 2019-03-19 outline/outline.tex
@@
 	\center
-
 	\textsc{\LARGE University of Minnesota}\\[0.35cm]
 	\textsc{\Large SENG 5852}\\[1.5cm]
-
-	{\huge\bfseries Analysis of Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
+	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
 	\textsc{\Large Research Paper Outline}\\[1cm] 
-
 	\textsc{\large\author
@@
 	}
-
 	\vfill\vfill\vfill
@@
 \newpage
-\section{Abstract}
 
 \section{Introduction}
+
 \subsection{Thesis Statement}
-\subsection{Purpose}
+The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.
+
+\subsection{Purpose Statement}
+Software engineering has for two decades, contemplated and experimented with the concept of distributing software in faster release cycles and have attempted to do so without sacrificing reliability and security.
+In attempt to achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment.
+The traditional methods of software development no longer meets the need of businesses that -- now more than ever -- want to proactively engage and retain customers.
+The organizational transition to Agile practices demands a large mentality change, requiring individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units as opposed to large modules developed by siloed units.
 
 \section{Body}
-	\subsection{Differences of Interpretation \& Implementation}
 	\subsection{What is Continuous Integration, Delivery, \& Deployment}
 		\subsubsection{Inherently Agile}
+		Explain what Agile is and how it ties in with CI/CDE/CD
 		\subsubsection{Continuous Integration}
+		Explain what CI is
 		\subsubsection{Continuous Delivery}
+		Explain what CDE is
 		\subsubsection{Continuous Deployment}
+		Explain what CD is
+
+	\subsection{Differences of Interpretation \& Implementation}
+		\subsubsection{Viewpoint of Software Professionals}
+		Explain how software professionals interpret and implement CI/CD/CDE
+		\subsubsection{Viewpoint of Academic Researchers}
+		Explain how academic researchers interpret and how CI/CD/CDE should be implemented
+		\subsubsection{Effort to Collaborate}
+		Explain the uncollaborative phenomena of developers and researchers as well as the ongoing effort to bridge the gap
+
+	\subsection{Benefits of Continuous Integration, Delivery, \& Deployment}
+		\subsubsection{Self-healing Systems}
+		Explain the metrics and tools that software professionals use to mitigate having to manually fix software issues
+		\subsubsection{Reduce Risk}
+		Explain how continuous software engineering reduces risk in systems 
+		\subsubsection{Faster Release Cycles}
+		Explain how faster release cycles are achieved
+		\subsubsection{Overall Reduction of Cost}
+		Explain why all of the above will reduce cost
+
 	\subsection{Struggles of Traceability}
-	\subsection{Paradigm Shift in Leadership}
+		\subsubsection{Importance}
+		Explain the importance of traceability in the software engineering community
+		\subsubsection{Problem of Mapping}
+		Explain the problem of mapping requirements to implemented code and the converse
+		\subsubsection{Eiffel Framework}
+		Explain the proposed solution to address traceability issues in CI/CDE/CD environments
+
+	\subsection{Transition an Agile Environment}
+		\subsubsection{The Effect of Organizational Change to Agile}
+		Explain the problems businesses face attempting to switch to Agile practices
+		\subsubsection{General Roles}
+		Explain typical roles that each individual plays in an Agile environment
+		\subsubsection{Paradigm Shift in Leadership}
+		Explain how leadership has changed as a result of Agile
 
 \section{Conclusion}
+	\subsection{Rephrase Thesis Statement}
+	\subsection{Closing Statement}
 
+\newpage
 \section{Bibliography}

### 2019-03-21 outline/outline.tex
Add annotated bibliography

@@
 	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
-	\textsc{\Large Research Paper Outline}\\[1cm] 
+	\textsc{\Large Outline}\\[1cm] 
 	\textsc{\large\author
@@
 In attempt to achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment.
-The traditional methods of software development no longer meets the need of businesses that -- now more than ever -- want to proactively engage and retain customers.
+The traditional methods of software development no longer meets the need of businesses that -- now more than ever -- want to proactively engage and retain their customers.
 The organizational transition to Agile practices demands a large mentality change, requiring individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units as opposed to large modules developed by siloed units.

### 2019-03-21 outline/outline.tex
Change outline

--- 2019-03-19 outline/outline.tex
@@
 \usepackage[T1]{fontenc}
+\usepackage{enumitem}
 \usepackage[format=plain, font=it]{caption}
@@
 	\center
-
 	\textsc{\LARGE University of Minnesota}\\[0.35cm]
 	\textsc{\Large SENG 5852}\\[1.5cm]
-
-	{\huge\bfseries The Race to Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
-	\textsc{\Large Research Paper Outline}\\[1cm]
-
+	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
+	\textsc{\Large Outline}\\[1cm] 
 	\textsc{\large\author
@@
 \subsection{Thesis Statement}
-The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software development.
+The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.
 
 \subsection{Purpose Statement}
-Software engineering has for two decades, contemplated and experimented with the concept of distributing software faster and better, without sacrificing reliability and security.
-There is a widespread movement in the technical community to advocate for using Agile practices to achieve such a feat, and in particular: continuous integration, delivery, and deployment.
-The traditional methods of software development no longer meets the need of businesses that want to proactively engage and retain customers.
-The organizational transition to Agile practices demands a large mentality change, understanding software as small increments developed with cross-collaboration of small team units as opposed to large modules developed by extensive siloed units.
+Software engineering has for two decades, experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security.
+To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment.
+The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers.
+The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.
 
 \section{Body}
-	\subsection{Differences of Interpretation \& Implementation}
 	\subsection{What is Continuous Integration, Delivery, \& Deployment}
 		\subsubsection{Inherently Agile}
+		\begin{itemize}[noitemsep]
+			\item What is Agile? 
+			\item What are the core ideas of Agile?
+			\item How does Agile tie in with CI/CDE/CD?
+		\end{itemize}
+		\vspace{-7mm}
 		\subsubsection{Continuous Integration}
+		\begin{itemize}[noitemsep]
+			\item What does CI mean?
+		\end{itemize}
 		\subsubsection{Continuous Delivery}
+		\begin{itemize}[noitemsep]
+			\item What does CDE mean?
+		\end{itemize}
 		\subsubsection{Continuous Deployment}
+		\begin{itemize}[noitemsep]
+			\item What does CD mean?
+		\end{itemize}
+
+	\subsection{Differences of Interpretation \& Implementation}
+		\subsubsection{Viewpoint of Software Professionals}
+		\begin{itemize}[noitemsep]
+			\item How do software professionals interpret and implement CI/CD/CDE?
+		\end{itemize}
+		\subsubsection{Viewpoint of Academic Researchers}
+		\begin{itemize}[noitemsep]
+			\item How do academic researchers interpret and believe how CI/CD/CDE should be implemented?
+		\end{itemize}
+		\subsubsection{Collaboration Effort}
+		\begin{itemize}[noitemsep]
+			\item What effort is there to bridge the phenomena of non-collaboration between developers and researchers?
+		\end{itemize}
+
+	\subsection{Benefits of Continuous Integration, Delivery, \& Deployment}
+		\subsubsection{Self-healing Systems}
+		\begin{itemize}[noitemsep]
+			\item What are the metrics and tools that software professionals use to mitigate having to manually fix software issues?
+			\item How do these self-healing systems work?
+		\end{itemize}
+		\subsubsection{Reduce Risk}
+		\begin{itemize}[noitemsep]
+			\item How does continuous software engineering reduces risk in systems?
+		\end{itemize}
+		\subsubsection{Faster Release Cycles}
+		\begin{itemize}[noitemsep]
+			\item How are faster release cycles are achieved?
+		\end{itemize}
+		\subsubsection{Overall Cost Reduction}
+		\begin{itemize}[noitemsep]
+			\item Why will all of the above will reduce cost?
+		\end{itemize}
+
 	\subsection{Struggles of Traceability}
-	\subsection{Paradigm Shift in Leadership}
-	naturally forming resistance from individuals from within.
+		\subsubsection{Importance}
+		\begin{itemize}[noitemsep]
+			\item What is the importance of traceability for the software engineering community?
+		\end{itemize}
+		\subsubsection{Problem of Mapping}
+		\begin{itemize}[noitemsep]
+			\item What is the problem of mapping requirements to implemented code and the converse?
+		\end{itemize}
+		\subsubsection{Eiffel Framework}
+		\begin{itemize}[noitemsep]
+			\item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
+		\end{itemize}
+
+	\subsection{Transition an Agile Environment}
+		\subsubsection{The Effect of Organizational Change to Agile}
+		\begin{itemize}[noitemsep]
+			\item What are the problems that businesses face in attempt to switch to Agile practices?
+		\end{itemize}
+		\subsubsection{Roles in Agile}
+		\begin{itemize}[noitemsep]
+			\item What are typical roles that each individual plays in an Agile environment? 
+			\item Why do these roles exist?
+		\end{itemize}
+		\subsubsection{Paradigm Shift in Leadership}
+		\begin{itemize}[noitemsep]
+			\item How has leadership changed as a result of Agile?
+		\end{itemize}
 
 \section{Conclusion}
+	\subsection{Rephrase Thesis Statement}
+	\subsection{Closing Statement}
 

### 2019-03-23 outline/outline.tex
Add paper

@@
 \usepackage{enumitem}
-\usepackage[format=plain, font=it]{caption}
 \usepackage{mathpazo}
-\usepackage{biblatex}
 
@@
 			\item What is Agile? 
+			\begin{itemize}
+				\item
+			\end{itemize}
 			\item What are the core ideas of Agile?
+			\begin{itemize}
+				\item
+			\end{itemize}
 			\item How does Agile tie in with CI/CDE/CD?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What does CI mean?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What does CDE mean?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What does CD mean?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item How do software professionals interpret and implement CI/CD/CDE?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item How do academic researchers interpret and believe how CI/CD/CDE should be implemented?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What effort is there to bridge the phenomena of non-collaboration between developers and researchers?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What are the metrics and tools that software professionals use to mitigate having to manually fix software issues?
+			\begin{itemize}
+				\item
+			\end{itemize}
 			\item How do these self-healing systems work?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item How does continuous software engineering reduces risk in systems?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item How are faster release cycles are achieved?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item Why will all of the above will reduce cost?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What is the importance of traceability for the software engineering community?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What is the problem of mapping requirements to implemented code and the converse?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What are the problems that businesses face in attempt to switch to Agile practices?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item What are typical roles that each individual plays in an Agile environment?
+			\begin{itemize}
+				\item
+			\end{itemize}
 			\item Why do these roles exist?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item How has leadership changed as a result of Agile?
+			\begin{itemize}
+				\item 
+			\end{itemize}
 		\end{itemize}
@@
 \section{Bibliography}
-\begin{thebibliography}{6}
-	\bibitem{Atkinson, Edwards} Atkinson, B., \& Edwards, D.
+\begin{thebibliography}{9}
+	\bibitem{atkinson} 
+	Atkinson, B., \& Edwards, D.
 (2018).
@@
 doi:\\\texttt{https://doi.org/10.1007/978-1-4842-3655-0}
-	\bibitem{Bosch} Bosch, J. (2014). Continuous Software Engineering. Cham: Springer International Publishing. doi:\\\texttt{https://doi-org.ezp1.lib.umn.edu/10.1007/978-3-319-11283-1.}
-	\bibitem{Stackify} Continuous Delivery, Deployment \& Integration: 20 Key Differences.
+
+	\bibitem{meyer}
+	Meyer, B. (2014). Agile! the Good, the Hype and the Ugly. Springer International Publishing. doi:\\\texttt{https://doi-org.ezp3.lib.umn.edu/10.1007/978-3-319-05155-0}
+
+	\bibitem{bosch} 
+	Bosch, J. (2014). Continuous Software Engineering. Springer International Publishing. doi:\\\texttt{https://doi-org.ezp1.lib.umn.edu/10.1007/978-3-319-11283-1.}
+
+	\bibitem{stackify} 
+	Continuous Delivery, Deployment \& Integration: 20 Key Differences.
 (2018, June 04).
 Retrieved from \\\texttt{https://stackify.com/continuous-delivery-vs-continuous-\\deployment-vs-continuous-integration}
-	\bibitem{Shahin, Babar, Zhu} Shahin, M., Babar, M.
+
+	\bibitem{shahin} 
+	Shahin, M., Babar, M.
 A., \& Zhu, L.
@@
 doi:\\\texttt{10.1109/access.2017.2685629}
-	\bibitem{Stahl} St\aa hl, D. (2017). Large Scale Continuous Integration and Delivery: Making Great Software Better and Faster. [Groningen]: University of Groningen.
-	\bibitem{Stahl, Hallen, Bosch} St\aa hl, D., Hall\'{e}n, K., \& Bosch, J.
+
+	\bibitem{groningen} St\aa hl, D. (2017). 
+	Large Scale Continuous Integration and Delivery: Making Great Software Better and Faster. [Groningen]: University of Groningen.
+
+	\bibitem{stahl} 
+	St\aa hl, D., Hall\'{e}n, K., \& Bosch, J.
 (2016).

### 2019-03-23 paper/paper.tex
Initial commit
Add paper

--- 2019-03-19 outline/outline.tex
@@
 	\center
-
 	\textsc{\LARGE University of Minnesota}\\[0.35cm]
 	\textsc{\Large SENG 5852}\\[1.5cm]
-
-	{\huge\bfseries Analysis of Continuous Integration, Delivery, \& Deployment}\\[0.35cm]	
-	\textsc{\Large Research Paper Outline}\\[1cm]
-
+	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
+	\textsc{\Large Research Paper}\\[1cm] 
 	\textsc{\large\author
@@
 
+\tableofcontents
 \newpage
-\section{Abstract}
 
 \section{Introduction}
-\subsection{Thesis Statement}
-\subsection{Purpose}
+The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.
+Software engineering has for two decades, experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security.
+To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment.
+The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers.
+The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.
 
 \section{Body}
-	\subsection{Differences of Interpretation \& Implementation}
 	\subsection{What is Continuous Integration, Delivery, \& Deployment}
 		\subsubsection{Inherently Agile}
+		\begin{itemize}[noitemsep]
+			\item What is Agile? 
+			\item What are the core ideas of Agile?
+			\item How does Agile tie in with CI/CDE/CD?
+		\end{itemize}
+		\vspace{-7mm}
 		\subsubsection{Continuous Integration}
+		\begin{itemize}[noitemsep]
+			\item What does CI mean?
+		\end{itemize}
 		\subsubsection{Continuous Delivery}
+		\begin{itemize}[noitemsep]
+			\item What does CDE mean?
+		\end{itemize}
 		\subsubsection{Continuous Deployment}
+		\begin{itemize}[noitemsep]
+			\item What does CD mean?
+		\end{itemize}
+
+	\subsection{Differences of Interpretation \& Implementation}
+		\subsubsection{Viewpoint of Software Professionals}
+		\begin{itemize}[noitemsep]
+			\item How do software professionals interpret and implement CI/CD/CDE?
+		\end{itemize}
+		\subsubsection{Viewpoint of Academic Researchers}
+		\begin{itemize}[noitemsep]
+			\item How do academic researchers interpret and believe how CI/CD/CDE should be implemented?
+		\end{itemize}
+		\subsubsection{Collaboration Effort}
+		\begin{itemize}[noitemsep]
+			\item What effort is there to bridge the phenomena of non-collaboration between developers and researchers?
+		\end{itemize}
+
+	\subsection{Benefits of Continuous Integration, Delivery, \& Deployment}
+		\subsubsection{Self-healing Systems}
+		\begin{itemize}[noitemsep]
+			\item What are the metrics and tools that software professionals use to mitigate having to manually fix software issues?
+			\item How do these self-healing systems work?
+		\end{itemize}
+		\subsubsection{Reduce Risk}
+		\begin{itemize}[noitemsep]
+			\item How does continuous software engineering reduces risk in systems?
+		\end{itemize}
+		\subsubsection{Faster Release Cycles}
+		\begin{itemize}[noitemsep]
+			\item How are faster release cycles are achieved?
+		\end{itemize}
+		\subsubsection{Overall Cost Reduction}
+		\begin{itemize}[noitemsep]
+			\item Why will all of the above will reduce cost?
+		\end{itemize}
+
 	\subsection{Struggles of Traceability}
-	\subsection{Paradigm Shift in Leadership}
+		\subsubsection{Importance}
+		\begin{itemize}[noitemsep]
+			\item What is the importance of traceability for the software engineering community?
+		\end{itemize}
+		\subsubsection{Problem of Mapping}
+		\begin{itemize}[noitemsep]
+			\item What is the problem of mapping requirements to implemented code and the converse?
+		\end{itemize}
+		\subsubsection{Eiffel Framework}
+		\begin{itemize}[noitemsep]
+			\item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
+		\end{itemize}
+
+	\subsection{Transition an Agile Environment}
+		\subsubsection{The Effect of Organizational Change to Agile}
+		\begin{itemize}[noitemsep]
+			\item What are the problems that businesses face in attempt to switch to Agile practices?
+		\end{itemize}
+		\subsubsection{Roles in Agile}
+		\begin{itemize}[noitemsep]
+			\item What are typical roles that each individual plays in an Agile environment? 
+			\item Why do these roles exist?
+		\end{itemize}
+		\subsubsection{Paradigm Shift in Leadership}
+		\begin{itemize}[noitemsep]
+			\item How has leadership changed as a result of Agile?
+		\end{itemize}
 
 \section{Conclusion}
+	\subsection{Rephrase Thesis Statement}
+	\subsection{Closing Statement}
 
+\newpage
 \section{Bibliography}

### 2019-03-27 outline/outline.tex
Add annotation style & common bibliography

--- 2019-03-21 outline/outline.tex
@@
 \usepackage{enumitem}
-\usepackage[format=plain, font=it]{caption}
 \usepackage{mathpazo}
-\usepackage{biblatex}
+\usepackage[hyphens,spaces,obeyspaces]{url}
+\usepackage{apacite}
 
@@
 			\item What is Agile?
+			\begin{itemize}
+				\item
+			\end{itemize}
 			\item What are the core ideas of Agile?
+			\begin{itemize}
+				\item
+			\end{itemize}
 			\item How does Agile tie in with CI/CDE/CD?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 			\item How has leadership changed as a result of Agile?
+			\begin{itemize}
+				\item
+			\end{itemize}
 		\end{itemize}
@@
 \section{Bibliography}
-\begin{thebibliography}{6}
-	\bibitem{Atkinson, Edwards} Atkinson, B., \& Edwards, D.
-(2018).
-Generic Pipelines Using Docker: The DevOps Guide to Building Reusable, Platform Agnostic CI/CD Frameworks.
-Berkeley, CA: Apress.
-doi:\\\texttt{https://doi.org/10.1007/978-1-4842-3655-0}
-	\bibitem{Bosch} Bosch, J. (2014). Continuous Software Engineering. Cham: Springer International Publishing. doi:\\\texttt{https://doi-org.ezp1.lib.umn.edu/10.1007/978-3-319-11283-1.}
-	\bibitem{Stackify} Continuous Delivery, Deployment \& Integration: 20 Key Differences.
-(2018, June 04).
-Retrieved from \\\texttt{https://stackify.com/continuous-delivery-vs-continuous-\\deployment-vs-continuous-integration}
-	\bibitem{Shahin, Babar, Zhu} Shahin, M., Babar, M.
-A., \& Zhu, L.
-(2017).
-Continuous Integration, Delivery and Deployment: A Systematic Review on Approaches, Tools, Challenges and Practices.
-IEEE Access, 5, 3909-3943.
-doi:\\\texttt{10.1109/access.2017.2685629}
-	\bibitem{Stahl} St\aa hl, D. (2017). Large Scale Continuous Integration and Delivery: Making Great Software Better and Faster. [Groningen]: University of Groningen.
-	\bibitem{Stahl, Hallen, Bosch} St\aa hl, D., Hall\'{e}n, K., \& Bosch, J.
-(2016).
-Achieving traceability in large scale continuous integration and delivery deployment, usage and validation of the eiffel framework.
-Empirical Software Engineering, 22(3), 967-995.
-doi:\\\texttt{10.1007/s10664-016-9457-1}
-\end{thebibliography}
+\nocite{*}
+\bibliographystyle{apacite}
+\bibliography{../bibliography}
 

### 2019-05-09 paper/paper.tex
WIP: Define Agile

@@
 \usepackage{enumitem}
-\usepackage[format=plain, font=it]{caption}
 \usepackage{mathpazo}
-\usepackage{biblatex}
+\usepackage{graphicx}
+\usepackage[hyphens,spaces,obeyspaces]{url}
+\usepackage{apacite}
 
@@
 	\textsc{\Large SENG 5852}\\[1.5cm]
-	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
+	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: What Does It Mean?}\\[0.35cm]	
 	\textsc{\Large Research Paper}\\[1cm] 
-	\textsc{\large\author
-		LLue Xiong\\
+	\textsc{\large\author\
+		Lue Xiong\\
 	}
@@
 
-\section{Introduction}
+\section{Cultural Shift in the Software Industry}
 The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.
+
 Software engineering has for two decades, experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security.
@@
 
-\section{Body}
-	\subsection{What is Continuous Integration, Delivery, \& Deployment}
-		\subsubsection{Inherently Agile}
+\section{Born from Agile}
+The word 'Agile' can be quite a jumbled terminology depending who a person talks to.
+Software professionals have their own experiences and stories of using it in their day-to-day work practices with varying degrees of opinions and outcomes.
+The Agile Manifesto is a declaration of the principles of Agile, which has a principle stating that the highest priority is satisfying customers with early and often continuous delivery \cite[p.
+~50]{meyer_2014}.
+It is apparent however, that at the heart of Agile is the value of producing software at a quick and efficient pace, without a sacrifice to a team's sustainability.
+One such software development method that has been existent for over two decades, and fundamentally an expression of the principles of the Agile Manifesto,is Extreme Programming (XP).
+
+Extreme Programming involves a set of practices including test-first development, automated testing, fast release cycles, refactoring, continuous integration, and among other things.
+Software professionals have embraced these set of practices for its effectiveness, even if arbitrarily and selectively picking from its' set.
+Bertrand Meyer, a well-respected individual in the software engineering community, considers many of the XP practices to be 'brilliant'; even going as far as to say that the practices of continuous integration and testing are major factors for the success of modern software projects \cite[p.
+~154]{meyer_2014}.
+Software professionals and organizations have embodied these ideals to keep up with the demands of the software market, and have effectively put them into action.
+
+Of the ideal software practices come commonly known and used vocabulary: continuous integration, delivery, and deployment.
+Many software professionals however, have misunderstood the above vocabulary and at times, infuse them as one concept without careful and thoughtful distinction.
+It would therefore, be wise to define each component for what they represent and why it matters.
+
 		\begin{itemize}[noitemsep]
 			\item What is Agile?
+			\begin{itemize}
+				\item \cite{bosch_2014} \& \cite{meyer_2014}
+			\end{itemize}
 			\item What are the core ideas of Agile?
+			\begin{itemize}
+				\item \cite{meyer_2014}
+			\end{itemize}
 			\item How does Agile tie in with CI/CDE/CD?
+			\begin{itemize}
+				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What does CI mean?
+			\begin{itemize}
+				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What does CDE mean?
+			\begin{itemize}
+				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What does CD mean?
+			\begin{itemize}
+				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item How do software professionals interpret and implement CI/CD/CDE?
+			\begin{itemize}
+				\item \cite{atkinson_edwards_2018} \& \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item How do academic researchers interpret and believe how CI/CD/CDE should be implemented?
+			\begin{itemize}
+				\item \cite{bosch_2014}, \cite{shahin_babar_zhu_2017}, \& \cite{stahl_2017}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What effort is there to bridge the phenomena of non-collaboration between developers and researchers?
+			\begin{itemize}
+				\item \cite{bosch_2014} \& \cite{stahl_2017}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What are the metrics and tools that software professionals use to mitigate having to manually fix software issues?
+			\begin{itemize}
+				\item \cite{bosch_2014}
+			\end{itemize}
 			\item How do these self-healing systems work?
+			\begin{itemize}
+				\item \cite{bosch_2014}
 			\end{itemize}
-		\subsubsection{Reduce Risk}
+		\end{itemize}
+		\subsubsection{Risk Reduction}
 		\begin{itemize}[noitemsep]
 			\item How does continuous software engineering reduces risk in systems?
+			\begin{itemize}
+				\item \cite{atkinson_edwards_2018}, \cite{bosch_2014}, \cite{stackify_2018}, \& \cite{stahl_2017} \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item How are faster release cycles are achieved?
+			\begin{itemize}
+				\item \cite{atkinson_edwards_2018}, \cite{bosch_2014}, \cite{stackify_2018}, \& \cite{stahl_2017} \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item Why will all of the above will reduce cost?
+			\begin{itemize}
+				\item \cite{atkinson_edwards_2018}, \cite{bosch_2014}, \cite{stackify_2018}, \& \cite{stahl_2017} \cite{stackify_2018}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What is the importance of traceability for the software engineering community?
+			\begin{itemize}
+				\item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What is the problem of mapping requirements to implemented code and the converse?
+			\begin{itemize}
+				\item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
+			\begin{itemize}
+				\item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What are the problems that businesses face in attempt to switch to Agile practices?
+			\begin{itemize}
+				\item \cite{bosch_2014} \& \cite{meyer_2014}
+			\end{itemize}
 		\end{itemize}
@@
 			\item What are typical roles that each individual plays in an Agile environment?
+			\begin{itemize}
+				\item \cite{bosch_2014} \& \cite{meyer_2014}
+			\end{itemize}
 			\item Why do these roles exist?
+			\begin{itemize}
+				\item \cite{bosch_2014} \& \cite{meyer_2014}
+			\end{itemize}
 		\end{itemize}
@@
 			\item How has leadership changed as a result of Agile?
+			\begin{itemize}
+				\item \cite{bosch_2014}
+			\end{itemize}
 		\end{itemize}

### 2019-05-10 paper/paper.tex
Define CI/CDE/CD

@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[12pt,a4paper]{article}
 
@@
 	\textsc{\Large SENG 5852}\\[1.5cm]
-	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: What Does It Mean?}\\[0.35cm]	
+	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: What Do They Mean?}\\[0.35cm]	
 	\textsc{\Large Research Paper}\\[1cm] 
@@
 
-\section{Cultural Shift in the Software Industry}
+\section{Introduction}
 The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.
@@
 
-\section{Born from Agile}
+\section{Constitution of Continuous Software Engineering Practices}
 The word 'Agile' can be quite a jumbled terminology depending who a person talks to.
-Software professionals have their own experiences and stories of using it in their day-to-day work practices with varying degrees of opinions and outcomes.
-The Agile Manifesto is a declaration of the principles of Agile, which has a principle stating that the highest priority is satisfying customers with early and often continuous delivery \cite[p.
+Software professionals have their own experiences and stories of using it in their day-to-day work with varying degrees of opinions and outcomes.
+The Agile Manifesto is a declaration of the principles of Agile, which attempts to alleviate any misunderstanding of what it means to be Agile in a software context.
+One principle of the Agile Manifesto states that the highest priority is satisfying customers with early and often continuous delivery \cite[p.
 ~50]{meyer_2014}.
-It is apparent however, that at the heart of Agile is the value of producing software at a quick and efficient pace, without a sacrifice to a team's sustainability.
-One such software development method that has been existent for over two decades, and fundamentally an expression of the principles of the Agile Manifesto,is Extreme Programming (XP).
+It is apparent that at the heart of Agile is the value of producing software quickly and efficiently, without sacrificing a team's sustainability.
+One such software development method that has been in existence for over two decades, and fundamentally a practical expression of the principles of the Agile Manifesto, is Extreme Programming (XP).
 
@@
 Software professionals have embraced these set of practices for its effectiveness, even if arbitrarily and selectively picking from its' set.
-Bertrand Meyer, a well-respected individual in the software engineering community, considers many of the XP practices to be 'brilliant'; even going as far as to say that the practices of continuous integration and testing are major factors for the success of modern software projects \cite[p.
+Bertrand Meyer -- a well-respected and influential individual in the software engineering community -- considers many of the XP practices to be 'brilliant.' He goes as far as to say that the practices of continuous integration and testing are major factors for the success of modern software projects \cite[p.
 ~154]{meyer_2014}.
-Software professionals and organizations have embodied these ideals to keep up with the demands of the software market, and have effectively put them into action.
+It is no wonder that many software professionals and organizations have turned to Agile and now embody Agile practices to keep up with the demands of the software market.
 
 Of the ideal software practices come commonly known and used vocabulary: continuous integration, delivery, and deployment.
-Many software professionals however, have misunderstood the above vocabulary and at times, infuse them as one concept without careful and thoughtful distinction.
+Many software professionals however, have misunderstood the these development practices and at times, infuse them as one concept without careful and thoughtful distinction.
 It would therefore, be wise to define each component for what they represent and why it matters.
 
-		\begin{itemize}[noitemsep]
-			\item What is Agile?
-			\begin{itemize}
-				\item \cite{bosch_2014} \& \cite{meyer_2014}
-			\end{itemize}
-			\item What are the core ideas of Agile?
-			\begin{itemize}
-				\item \cite{meyer_2014}
-			\end{itemize}
-			\item How does Agile tie in with CI/CDE/CD?
-			\begin{itemize}
-				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
-			\end{itemize}
-		\end{itemize}
-		\vspace{-7mm}
-		\subsubsection{Continuous Integration}
-		\begin{itemize}[noitemsep]
-			\item What does CI mean?
-			\begin{itemize}
-				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
-			\end{itemize}
-		\end{itemize}
-		\subsubsection{Continuous Delivery}
-		\begin{itemize}[noitemsep]
-			\item What does CDE mean?
-			\begin{itemize}
-				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
-			\end{itemize}
-		\end{itemize}
-		\subsubsection{Continuous Deployment}
-		\begin{itemize}[noitemsep]
-			\item What does CD mean?
-			\begin{itemize}
-				\item \cite{shahin_babar_zhu_2017} \& \cite{stackify_2018}
-			\end{itemize}
-		\end{itemize}
+Continuous integration is a practice entrusted to the active engagement of the members of a team developing code, of which they will participate by integrating and merging code to a source control management service such as GitHub; typically on a frequent basis.
+It contains an autonomous process that builds the software based on the new state of the code and verifies the software against a collection of tests.
+The important thing to note is that there is a quick feedback loop to the maintainers of the code based on the tests, determining whether any action is necessary to move forward.
+The main benefits to software organizations using continuous integration are shorter and faster release cycles, improvement of software product quality, and an increase of team productivity \cite[p.
+~3910]{shahin_babar_zhu_2017}.
+
+It is absolutely crucial to note that using continuous delivery is state-dependent practice on continuous integration.
+The purpose of continuous delivery is to provision the software product to an production-like environment meant for acceptance testing by stakeholders such as the customers.
+The stakeholders are the main drivers for the decision of whether the software product can go into a real production environment.
+In the case that it is accepted, a manual process will be used to deploy it to production.
+The benefits of continuous delivery include reduced deployment risks, faster user feedback, and overall lower project costs \cite[p.
+~3910-3911]{shahin_babar_zhu_2017}.
+
+The same state-dependence goes for continuous deployment as well; it cannot exist without continuous integration.
+There is also the implication that continuous delivery is a major part of continuous deployment.
+The distinguishing factor of continuous deployment versus continuous delivery is the extra step of an automated process of the deployment to production \cite[p.
+~3911]{shahin_babar_zhu_2017}.
+For this to be possible, the software must be verified against a robust and fully automated collection of test suites, assuring with high confidence that the software works as it is intended to by design.
+Rod Cope, CTO of Rogue Wave Software says that companies that use continuous deployment can push hundreds or even thousands of releases into production per day \cite{stackify_2018}.
+
+Software professionals however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another.
+For example, Kofi Senaya, Director of Product from Clearbridge Mobile says "continuous Integration means that when [developers] are working on the same code, they are building and unit-testing it to prevent any integration problems" \cite{stackify_2018}.
+The first misunderstanding from Kofi is that he implies continuous integration only runs unit tests against the source code.
+Other levels of testing such as integration and system testing can also be implemented for continuous integration.
+The second misunderstanding is the implication that unit tests will cover all cases of integration functionality.
+There is a reason that integration tests exist, and that is for testing that module-to-module interaction works as intended.
 

### 2019-05-10 paper/paper.tex
WIP

@@
 
-Software engineering has for two decades, experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security.
+The software engineering community has for a few decades experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security.
 To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment.
@@
 \section{Constitution of Continuous Software Engineering Practices}
-The word 'Agile' can be quite a jumbled terminology depending who a person talks to.
+The word 'Agile' can be quite a jumbled terminology depending whom a person talks to.
 Software professionals have their own experiences and stories of using it in their day-to-day work with varying degrees of opinions and outcomes.
@@
 
-Of the ideal software practices come commonly known and used vocabulary: continuous integration, delivery, and deployment.
-Many software professionals however, have misunderstood the these development practices and at times, infuse them as one concept without careful and thoughtful distinction.
-It would therefore, be wise to define each component for what they represent and why it matters.
+Of the ideal software practices that are commonly known and trending vocabulary -- continuous integration, delivery, and deployment -- come with the responsibility of defining them.
+Many software professionals, however, have misunderstood these development practices and at times, infuse them as one concept without careful and thoughtful distinction.
+It would, therefore, be wise to define each component for what they represent and why it matters.
 
@@
 It is absolutely crucial to note that using continuous delivery is state-dependent practice on continuous integration.
-The purpose of continuous delivery is to provision the software product to an production-like environment meant for acceptance testing by stakeholders such as the customers.
+The purpose of continuous delivery is to deploy a software product to a production-like environment meant for acceptance testing by stakeholders such as the customers.
 The stakeholders are the main drivers for the decision of whether the software product can go into a real production environment.
@@
 
-Software professionals however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another.
+Software professionals, however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another.
 For example, Kofi Senaya, Director of Product from Clearbridge Mobile says "continuous Integration means that when [developers] are working on the same code, they are building and unit-testing it to prevent any integration problems" \cite{stackify_2018}.
@@
 There is a reason that integration tests exist, and that is for testing that module-to-module interaction works as intended.
+The third misunderstanding is stating that the developers are building and unit testing the software.
+The statement assumes that continuous integration is a manual process by which the developers partake in compiling and then running tests against the software.
+Kofi then goes on to say that "the code is verified by the automated build which allows teams to identify problems" \cite{stackify_2018}, which conflicts with the previous statement.
+It is clear that explaining the uniquity of these continuous software engineering practices is a challenge for software professionals.
+
+An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of software developers and software researchers non-collaboration.
 

### 2019-05-10 paper/paper.tex
WIP: dev vs. researcher

@@
 \usepackage{graphicx}
+\usepackage{caption}
 \usepackage[hyphens,spaces,obeyspaces]{url}
@@
 Rod Cope, CTO of Rogue Wave Software says that companies that use continuous deployment can push hundreds or even thousands of releases into production per day \cite{stackify_2018}.
+The intent behind continuous deployment is deliver a working product to customers as fast as possible, hence the heavy emphasis on automation.
+Upon asking a software architect about the practice, who chose not be to named, said, "let me put it this way, if I want a pony, then give me a damn pony.
+That's how simple it should be" (anonymous, personal communication, April 30, 2019).
+Although spoken quite metaphorically, the architect does get across the idea that if the continuous deployment system was built the way it was supposed to, a 'want' should in fact result in a ready-to-use product.
 
@@
 Kofi then goes on to say that "the code is verified by the automated build which allows teams to identify problems" \cite{stackify_2018}, which conflicts with the previous statement.
-It is clear that explaining the uniquity of these continuous software engineering practices is a challenge for software professionals.
+It is clear that explaining the intricacies of these continuous software engineering practices is a challenge for software professionals.
 
-An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of software developers and software researchers non-collaboration.
+An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of non-collaboration between software developers and academic researchers.
+Computer scientist and software engineering professor, Jan Bosch, states that even the greatest developers in the software industry view top academic researchers as people who give insignificant learning value and the converse being true as well \cite[p.
+~29]{bosch_2014}.
+In particular, top researchers do not believe that top developers contribute much to their body of research.
+The intrinsic difference between the developer and researcher is in how they view the value of software engineering.
+Developers by nature of their work are expected to produce software in a timely business-oriented manner, whereas researchers are focused on the insights that data analysis can accomplish.
+
+There has been effort to bridge the gap between the two groups but this effort has been far from trivial.
+
+% \begin{figure}[ht!]
+% 	\begin{center}
+% 		\includegraphics[width=.75\textwidth]{images/research.png}
+% 	\end{center}
+% 	\captionsetup{justification=centering}
+% 	\caption{Success Factor Model for Academia-Industry Collaboration, Adapted from \protect\citeA[p. ~30]{bosch_2014}}
+% 	\label{academia_industry}
+% \end{figure}
 

### 2019-05-11 paper/paper.tex
WIP: Closing statement

@@
 \usepackage{apacite}
+\usepackage{etoolbox}
 
@@
 
-\tableofcontents
 \newpage
-
 \section{Introduction}
@@
 
-\section{Constitution of Continuous Software Engineering Practices}
+\section{Continuous Software Engineering}
 The word 'Agile' can be quite a jumbled terminology depending whom a person talks to.
@@
 
-Continuous integration is a practice entrusted to the active engagement of the members of a team developing code, of which they will participate by integrating and merging code to a source control management service such as GitHub; typically on a frequent basis.
-It contains an autonomous process that builds the software based on the new state of the code and verifies the software against a collection of tests.
+\begin{figure}[ht!]
+    \includegraphics[width=1.02\textwidth]{images/ci_cde_cd.png}
+    \captionsetup{justification=centering, labelfont=bf}
+    \caption{The relationship between continuous integration, delivery and deployment, Adapted from \protect\citeA[p. ~3911]{shahin_babar_zhu_2017}}
+    \label{ci_cde_cd}
+\end{figure}
+
+Continuous integration is a practice entrusted to the active engagement of the members of a team developing code, of which they participate by integrating and merging code to a source control management service such as GitHub; typically on a frequent basis.
+It contains an automated process that builds the software based on the new state of the code and verifies the software against a collection of tests.
 The important thing to note is that there is a quick feedback loop to the maintainers of the code based on the tests, determining whether any action is necessary to move forward.
@@
 
-It is absolutely crucial to note that using continuous delivery is state-dependent practice on continuous integration.
-The purpose of continuous delivery is to deploy a software product to a production-like environment meant for acceptance testing by stakeholders such as the customers.
+It is absolutely crucial to note from Figure~\ref{ci_cde_cd} that using continuous delivery is state-dependent practice on continuous integration.
+The purpose of continuous delivery is to deploy a software product to a production-like environment meant for acceptance testing by stakeholders such as the customers, but only after it has been verified to work by the continuous integration process.
 The stakeholders are the main drivers for the decision of whether the software product can go into a real production environment.
-In the case that it is accepted, a manual process will be used to deploy it to production.
+In the case that it is accepted, a manual process will be used to deploy the software into production.
 The benefits of continuous delivery include reduced deployment risks, faster user feedback, and overall lower project costs \cite[p.
@@
 Rod Cope, CTO of Rogue Wave Software says that companies that use continuous deployment can push hundreds or even thousands of releases into production per day \cite{stackify_2018}.
-The intent behind continuous deployment is deliver a working product to customers as fast as possible, hence the heavy emphasis on automation.
+The intent behind continuous deployment is delivering a working product to customers as fast as possible, hence the heavy emphasis on automation.
 Upon asking a software architect about the practice, who chose not be to named, said, "let me put it this way, if I want a pony, then give me a damn pony.
 That's how simple it should be" (anonymous, personal communication, April 30, 2019).
-Although spoken quite metaphorically, the architect does get across the idea that if the continuous deployment system was built the way it was supposed to, a 'want' should in fact result in a ready-to-use product.
+Although spoken quite metaphorically, the architect does get across the idea that if the continuous deployment system was built the way it was supposed to, a 'want' should, in fact, result in a ready-to-use product.
 
@@
 Kofi then goes on to say that "the code is verified by the automated build which allows teams to identify problems" \cite{stackify_2018}, which conflicts with the previous statement.
+The conceptual integrity of continuous software engineering practices has yet to mature within the software industry.
 It is clear that explaining the intricacies of these continuous software engineering practices is a challenge for software professionals.
@@
 In particular, top researchers do not believe that top developers contribute much to their body of research.
-The intrinsic difference between the developer and researcher is in how they view the value of software engineering.
-Developers by nature of their work are expected to produce software in a timely business-oriented manner, whereas researchers are focused on the insights that data analysis can accomplish.
+The intrinsic difference between the developer and researcher is in how they view the values of software engineering as a means to a different end.
+Developers by nature of their work are expected to produce software in a timely business-oriented manner, wherein researchers are focused on the insights that data analysis can accomplish.
 
-There has been effort to bridge the gap between the two groups but this effort has been far from trivial.
+The implementation of continuous integration, delivery, and deployment is time-intensive and difficult as well as complex and inherently abstract.
+Among the many identified challenges for continuous practices are \cite[p.
+~3925-3927]{shahin_babar_zhu_2017}: lack of expertise and skill, lack of appropriate technologies, coordination and collaboration, increased business pressure and workload, improper test strategies, stateful design and code dependencies, resistance to change, and the list goes on.
+One of the distinct challenges of the identified challenges is the lack of expertise and skill.
+The traditional method of development typically required a developer to work isolation on features with a limited and familiar stack of technology.
+Developing continuous practices in contrast requires new and different technical skills, a heap of new and unfamiliar technology, and soft skills for an unprecedented level of collaboration across teams.
+Transitioning to such a different way of development is daunting for many and carries with it, a set of new engineering issues for developers to solve.
 
-% \begin{figure}[ht!]
-% 	\begin{center}
-% 		\includegraphics[width=.75\textwidth]{images/research.png}
-% 	\end{center}
-% 	\captionsetup{justification=centering}
-% 	\caption{Success Factor Model for Academia-Industry Collaboration, Adapted from \protect\citeA[p. ~30]{bosch_2014}}
-% 	\label{academia_industry}
-% \end{figure}
+A particular issue that plagues the software industry is the traceability of requirements in the context of using continuous practices.
 
-    \subsection{Differences of Interpretation \& Implementation}
-        \subsubsection{Viewpoint of Software Professionals}
-        \begin{itemize}[noitemsep]
-            \item How do software professionals interpret and implement CI/CD/CDE?
-            \begin{itemize}
-                \item \cite{atkinson_edwards_2018} \& \cite{stackify_2018}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Viewpoint of Academic Researchers}
-        \begin{itemize}[noitemsep]
-            \item How do academic researchers interpret and believe how CI/CD/CDE should be implemented?
-            \begin{itemize}
-                \item \cite{bosch_2014}, \cite{shahin_babar_zhu_2017}, \& \cite{stahl_2017}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Collaboration Effort}
-        \begin{itemize}[noitemsep]
-            \item What effort is there to bridge the phenomena of non-collaboration between developers and researchers?
-            \begin{itemize}
-                \item \cite{bosch_2014} \& \cite{stahl_2017}
-            \end{itemize}
-        \end{itemize}
+On the topic of continuous integration alone, Daniel Stahl points out the problems that the software industry is facing \cite[p. ~60]{stahl_2017}:
 
-    \subsection{Benefits of Continuous Integration, Delivery, \& Deployment}
-        \subsubsection{Self-healing Systems}
-        \begin{itemize}[noitemsep]
-            \item What are the metrics and tools that software professionals use to mitigate having to manually fix software issues?
-            \begin{itemize}
-                \item \cite{bosch_2014}
-            \end{itemize}
-            \item How do these self-healing systems work?
-            \begin{itemize}
-                \item \cite{bosch_2014}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Risk Reduction}
-        \begin{itemize}[noitemsep]
-            \item How does continuous software engineering reduces risk in systems?
-            \begin{itemize}
-                \item \cite{atkinson_edwards_2018}, \cite{bosch_2014}, \cite{stackify_2018}, \& \cite{stahl_2017} \cite{stackify_2018}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Faster Release Cycles}
-        \begin{itemize}[noitemsep]
-            \item How are faster release cycles are achieved?
-            \begin{itemize}
-                \item \cite{atkinson_edwards_2018}, \cite{bosch_2014}, \cite{stackify_2018}, \& \cite{stahl_2017} \cite{stackify_2018}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Overall Cost Reduction}
-        \begin{itemize}[noitemsep]
-            \item Why will all of the above will reduce cost?
-            \begin{itemize}
-                \item \cite{atkinson_edwards_2018}, \cite{bosch_2014}, \cite{stackify_2018}, \& \cite{stahl_2017} \cite{stackify_2018}
-            \end{itemize}
-        \end{itemize}
+\begin{quotation}
+    \textit{As the size of a software development effort increases several things tend to happen.
+The size of the code base increases, implying longer build times.
+The number and the scope of tests tend to increase, implying longer test times.
+This in turn leads to a decreased time frame in which to integrate one's changes...
+Furthermore, a great number of developers involved implies both an increased rate of changes and more people impacted by failed integrations.}
+\end{quotation}
+
+The software engineering community is still in the early stages of understanding and implementing continuous practices.
+It will take time for the community to find engineering standards for continuous practices to mitigate the risks while taking advantage of its' benefits.
 
@@
 
-    \subsection{Transition an Agile Environment}
-        \subsubsection{The Effect of Organizational Change to Agile}
-        \begin{itemize}[noitemsep]
-            \item What are the problems that businesses face in attempt to switch to Agile practices?
-            \begin{itemize}
-                \item \cite{bosch_2014} \& \cite{meyer_2014}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Roles in Agile}
-        \begin{itemize}[noitemsep]
-            \item What are typical roles that each individual plays in an Agile environment?
-            \begin{itemize}
-                \item \cite{bosch_2014} \& \cite{meyer_2014}
-            \end{itemize}
-            \item Why do these roles exist?
-            \begin{itemize}
-                \item \cite{bosch_2014} \& \cite{meyer_2014}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Paradigm Shift in Leadership}
-        \begin{itemize}[noitemsep]
-            \item How has leadership changed as a result of Agile?
-            \begin{itemize}
-                \item \cite{bosch_2014}
-            \end{itemize}
-        \end{itemize}
-
 \section{Conclusion}
-    \subsection{Rephrase Thesis Statement}
-    \subsection{Closing Statement}
 

### 2019-05-11 paper/paper.tex
Done

@@
 The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.
-
 The software engineering community has for a few decades experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security.
@@
 The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers.
-The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.
+The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-functional collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.
 
@@
 Of the ideal software practices that are commonly known and trending vocabulary -- continuous integration, delivery, and deployment -- come with the responsibility of defining them.
-Many software professionals, however, have misunderstood these development practices and at times, infuse them as one concept without careful and thoughtful distinction.
+Many software professionals, however, have misunderstood these development practices and at times, infuse them as non-differing concepts without careful and thoughtful distinction.
 It would, therefore, be wise to define each component for what they represent and why it matters.
@@
 
-An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of non-collaboration between software developers and academic researchers.
+An added layer of complexity that makes further refinement of what it means to do continuous software engineering more difficult is the well-documented phenomena of non-collaboration between software developers and academic researchers.
 Computer scientist and software engineering professor, Jan Bosch, states that even the greatest developers in the software industry view top academic researchers as people who give insignificant learning value and the converse being true as well \cite[p.
@@
 Developers by nature of their work are expected to produce software in a timely business-oriented manner, wherein researchers are focused on the insights that data analysis can accomplish.
+There has been little progress between the two groups but some effort has been made by the Software Center to create mutually beneficial and collaborative work on software engineering issues \cite[p.
+~31]{bosch_2014}.
+
+Alone on the topic of continuous integration, Daniel Stahl plainly points out the problems that the software industry is currently facing \cite[p. ~60]{stahl_2017}:
+
+\begin{quotation}
+    \textit{As the size of a software development effort increases several things tend to happen.
+The size of the code base increases, implying longer build times.
+The number and the scope of tests tend to increase, implying longer test times.
+This in turn leads to a decreased time frame in which to integrate one's changes...
+Furthermore, a great number of developers involved implies both an increased rate of changes and more people impacted by failed integrations.}
+\end{quotation}
+
+Continuous integration aims to solve these types of scaling issues but is a significant challenge to implement in its own right.
+There are many cases where organizations have successfully implemented continuous integration in a large-scale context despite the complexity.
+Stahl's findings from his case studies supports that a key enabler for success in implementing continuous integration is the communication of a shared vision within an organization, but should be further examined for legitimacy \cite[p.
+~86]{stahl_2017}.
+Bosch would argue that in an Agile environment, which continuous practices rightfully belongs, leadership culture needs to change to a more suitable style of support, rather than the old command and control style \cite[p.
+~209]{bosch_2014}.
 
@@
 
-A particular issue that plagues the software industry is the traceability of requirements in the context of using continuous practices.
-
-On the topic of continuous integration alone, Daniel Stahl points out the problems that the software industry is facing \cite[p. ~60]{stahl_2017}:
-
-\begin{quotation}
-    \textit{As the size of a software development effort increases several things tend to happen.
-The size of the code base increases, implying longer build times.
-The number and the scope of tests tend to increase, implying longer test times.
-This in turn leads to a decreased time frame in which to integrate one's changes...
-Furthermore, a great number of developers involved implies both an increased rate of changes and more people impacted by failed integrations.}
-\end{quotation}
-
+\section{Conclusion}
 The software engineering community is still in the early stages of understanding and implementing continuous practices.
-It will take time for the community to find engineering standards for continuous practices to mitigate the risks while taking advantage of its' benefits.
-
-    \subsection{Struggles of Traceability}
-        \subsubsection{Importance}
-        \begin{itemize}[noitemsep]
-            \item What is the importance of traceability for the software engineering community?
-            \begin{itemize}
-                \item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Problem of Mapping}
-        \begin{itemize}[noitemsep]
-            \item What is the problem of mapping requirements to implemented code and the converse?
-            \begin{itemize}
-                \item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
-            \end{itemize}
-        \end{itemize}
-        \subsubsection{Eiffel Framework}
-        \begin{itemize}[noitemsep]
-            \item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
-            \begin{itemize}
-                \item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
-            \end{itemize}
-        \end{itemize}
-
-\section{Conclusion}
+It will take time for the community to find engineering standards for continuous practices to mitigate the risks associated with it while taking advantage of its' benefits.
+It is important to further refine these engineering solutions as the software industry slowly transition to and embrace the Agile culture.
+It could very well be that in the near future -- in order to survive as an organization producing and selling software -- that Agile and its subset, continuous practices, become a necessity rather than just a different way of development.
+The consumers will be the decisive factor as more and more of them expect quality software products at a faster pace.
 
